Comparing characters

### 2017-07-17 Analysis/Character_difference/Comparing_characters.Rmd
Added formula in LaTeX

```{r, eval = FALSE}
# The latest version of devtools
if(!require(devtools)) install.packages("devtools")

## The latest version of dispRity 
install_github("TGuillerme/dispRity")
```

@@

![equation](http://www.sciweavers.org/tex2img.php?eq=1%20-%20%5Cleft%28%20%5Cfrac%7B%5Cmid%20%7B%5Cfrac%7B%5Cabs%7B%5Csum_%7Bi%7D%5E%7Bn%7D%28%5Cmid%20x_%7Bi%7D%20-%20y_%7Bi%7D%5Cmid%20%29%7D%7D%20%7Bn%7D-%5Cfrac%7B1%7D%7B2%7D%7D%20%5Cmid%20%20%7D%7B%5Cfrac%7B1%7D%7B2%7D%7D%5Cright%29&bc=White&fc=Black&im=jpg&fs=12&ff=arev&edit=0)
<!-- \begin{equation}
    1 - \left( \frac{\mid {\frac{\abs{\sum_{i}^{n}(\mid x_{i} - y_{i}\mid )}} {n}-\frac{1}{2}} \mid  }{\frac{1}{2}}\right)
\end{equation} -->

@@

```{r}
source("../../Functions/char.diff.R")
dyn.load("../../Functions/char.diff.so")
```

@@

```{r}
library(dispRity) ; set.seed(123)
# A random tree (coalescent)
tree <- rcoal(15)
# A morphological matrix (Mk model)
matrix <- sim.morpho(tree, 50, states = c(0.85, 0.15), rates = c(rgamma, rate = 10, shape = 5),
    invariant = FALSE)
# Checking matrix
check.morpho(matrix, tree)

>>>>

```{r, eval = TRUE}
library(dispRity) 
```

@@

$$1 - \left( \frac{\mid {\frac{\abs{\sum_{i}^{n}(\mid x_{i} - y_{i}\mid )}} {n}-\frac{1}{2}} \mid  }{\frac{1}{2}}\right)$$

@@

@@

```{r}
set.seed(0)
# A random tree (coalescent)
tree <- rcoal(15)
# A morphological matrix (Mk model)
matrix <- sim.morpho(tree, 50, states = c(0.85, 0.15), rates = c(rgamma, rate = 10, shape = 5),
    invariant = FALSE)
# Checking matrix
check.morpho(matrix, tree)
